Maximum likelihood estimation

### 2021-10-16 text/Rmd/maximum-liikelihood/maximum-likelihood.Rmd

![](http://www.pmean.com/new-images/03/mle1a.gif){width="352" height="272"}

@@

![](http://www.pmean.com/new-images/03/mle2a.gif){width="352" height="272"}

@@

![](http://www.pmean.com/new-images/03/mle3a.gif){width="352" height="272"}

@@

![](http://www.pmean.com/new-images/03/mle4a.gif){width="352" height="272"}

@@

![](http://www.pmean.com/new-images/03/mle5a.gif){width="352" height="272"}

@@

![](http://www.pmean.com/new-images/03/mle6.gif){width="94" height="52"}

@@

![](http://www.pmean.com/new-images/03/mle7.gif){width="367" height="62"}

@@

![](http://www.pmean.com/new-images/03/mle8.gif){width="212" height="62"}

@@

![](images/mle9.gif){width="298" height="51"}

>>>>

![](mle1a.gif){width="352" height="272"}

@@

![](mle2a.gif){width="352" height="272"}

@@

![](mle3a.gif){width="352" height="272"}

@@

![](mle4a.gif){width="352" height="272"}

@@

![](mle5a.gif){width="352" height="272"}

@@

![](mle6.gif){width="94" height="52"}

@@

![](mle7.gif){width="367" height="62"}

@@

![](mle8.gif){width="212" height="62"}

@@

![](mle9.gif){width="298" height="51"}
